%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                 %
%                     SECTION                     %
%                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgements}
\label{sec:sec012}

A special thanks for the support provided by Hugo Lencastre. We would like to thank Doctor Clara Aleluia, Doctor Gisela Andrade, Doctor Willian Schmitt, Doctor Ana Sofia Germano and Doctor Pedro Marques from the HFF for the generous support and medical expertise. Also, an immense thank for Doctor Cristina Ribeiro da Fonseca. My appreciation goes also to Bruno Cardoso and Bruno Dias for help and above all for the good companionship. Thanks to Professor Daniel Gon\c{c}alves, Professor Daniel Sim\~{o}es Lopes and Daniel Mendes for the technical inputs and network. Last but not least, thank to my advisors Professor Jacinto C. Nascimento and Professor Nuno Jardim Nunes. We also want to provide a special acknowledgment to Professor Ramtin Zargari Marandi who, among others, gave us important information and comments regarding the presented report. This work was partially supported by national funds through Funda\c{c}\~{a}o para a Ci\^{e}ncia e a Tecnologia (FCT) with reference UID/CEC/50021/2013 and Instituto Superior T\'{e}cnico (IST-ID) through the FCT/UID/EEA/50009/2013 project, BL89/2017-IST-ID grant. We would like to convey Hospital Fernando Fonseca (HFF) for the collaboration.