%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                 %
%                     SECTION                     %
%                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgements}
\label{sec:sec012}

A special thanks for the support and revisions provided by Hugo Lencastre and N\'{a}dia Mour\~{a}o.
We would like to thank Doctor Clara Aleluia, Doctor Gisela Andrade, Dr. Willian Schmitt, Dr. Ana Sofia Germano and Dr. Pedro Marques from the Hospital Fernando Fonseca for the generous support and medical expertise.
Also, an immense thank for Dr. Cristina Ribeiro da Fonseca.
My appreciation goes also to Bruno Cardoso and Bruno Dias for help and above all for the good companionship.
Thanks to Prof. Daniel Gon\c{c}alves, Prof. Daniel Sim\~{o}es Lopes and Daniel Mendes for the technical inputs and network.
Last but not least, thank to my advisors Prof. Jacinto C. Nascimento and Prof. Nuno Jardim Nunes.
We also want to provide a special acknowledgment to Prof. Ramtin Zargari Marandi who, among others, gave us important information and comments regarding the presented report.
This work was partially supported by national funds through Funda\c{c}\~{a}o para a Ci\^{e}ncia e a Tecnologia (FCT) with reference UID/CEC/50021/2013 and Instituto Superior T\'{e}cnico (IST-ID) through the FCT/UID/EEA/50009/2013 project, BL89/2017-IST-ID grant.
We would like to convey Hospital Fernando Fonseca for the collaboration.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%