%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                 %
%                     SECTION                     %
%                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Evaluation}
\label{sec:sec006}

The study followed the required ethical standards.
Specifically, the study complies with the provisions of the General Data Protection Regulation [Regulation (EU) 2016/279 of the European Parliament and of the Council of 27 April 2016], and follows the recommendations of the Declaration of Helsinki for research.
There are no risks and benefits associated with the users' participation.
User's participation is completely voluntary.

Quantitative and qualitative studies will be conducted with clinical experts and healthcare professionals.
Analysis will be performed by descriptive categorization statistics of statements.
In this document, results (Section~\ref{sec:sec011}) are being briefly described, but the evaluation process is further reported.

The raw data will be analyzed as follows.
In accordance with the recommendations~\cite{rahi2018investigating} of the two-stage procedure (Section~\ref{sec:sec003}), CFA will be used to test validity and reliability of the model~\cite{crede2019questionable}.
SEM will be used as a preferable technique to regression as it allows simultaneous analysis of all relationships through multiple regression, while also allowing for both observed and latent variables to be analyzed at the same time, and providing overall fit statistics~\cite{hair2017advanced}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%